---
title: "databaseforarti"
author: "Quillo"
date: "2024-03-10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

INSERT ALL REVIEWS DATA FRAME TO DATABASE

USED RMYSQL

```{r}
library(DBI)
library(odbc)
library(RMySQL)
library(dplyr,dbplyr)
```
connection <- dbConnect(RMySQL::MySQL(),
                        dsn="MariaDB-connection",
                        Server = "localhost",
                        dbname = "quillo_2c", 
                        user = "root", 
                        password = "") 


```{r}

library(readr)

artiFiveG <- read.csv("Arxivpaperson5G.csv")
tail(artiFiveG)

```

Writing Table to Database

```{r}

# dbWriteTable(connection, 'labact4Arti', articles, append = TRUE)

```

LISTING TABLES AND FIELDS

```{r}```

dbListTables(connection)
dbListFields(connection,'labact4Arti')


READING DATA FROM TABLE

```{r}```

artidata <- dbGetQuery(connection, "SELECT * FROM quillo_2c.labact4Arti")
glimpse(artidata)

